So you've decided to detonate helium

### 2020-04-30 sdc_applications/paper.tex
updates

Writing this out for two species, $X_\alpha$ and $X_\beta$, we have
\begin{equation}
\Uc = \left ( \begin{array}{c} \rho X_\alpha \\ \rho X_\beta \\ \rho E \\ \rho e \end{array} \right )
\end{equation}
We take the intermediate state to be ${\bf w} = (\rho, X_\alpha, X_\beta,
T)^\intercal$.

The Jacobian transformation $\partial \Uc/\partial {\bf w}$ is:
\begin{equation}
\frac{\partial \Uc}{\partial {\bf w}} = \left (
   \begin{array}{cccc}
       X_\alpha & \rho & 0 & 0\\
       X_\beta & 0 & \rho & 0 \\
       \rho e_\rho  + e + K &
                 \rho  e_{X_\alpha} & \rho e_{X_\beta} &
                 \rho e_T \\
       \rho e_\rho  + e  &
                 \rho  e_{X_\alpha} & \rho e_{X_\beta} &
                 \rho e_T
     \end{array}\right)
\end{equation}
where we use the following notation for compactness:
\begin{equation}
e_\rho = \dedrd \qquad 
e_T = \dedTd \qquad
e_{X_k} = \dedXd 
\end{equation}
and write the kinetic energy as $K = |\Ub|^2/2$.  We get the inverse
(computed via SymPy, see the included Jupyter notebook) is:

\begin{equation}
\renewcommand{\arraystretch}{1.5}
\frac{\partial {\bf w}}{\partial \Uc} = \left (
  \begin{array}{cccc}
   0  & 0  &  \frac{1}{K} & -\frac{1}{K} \\
   \frac{1}{\rho} & 0 & - \frac{X_\alpha}{\rho K} & \frac{X_\alpha}{\rho K} \\
   0 & \frac{1}{\rho} &  - \frac{X_\beta}{\rho K} & \frac{X_\beta}{\rho K} \\
   -\frac{e_{X_\alpha}}{\rho e_T} & -\frac{e_{X_\beta}}{\rho e_T} & 
   \frac{\sum_k X_{k} e_{X_k} - \rho e_\rho - e }{\rho e_T K}  &
   -\frac{\sum_k X_{k} e_{X_k} - \rho e_\rho - e - K}{ \rho e_T K}  \\
   \end{array}\right)
\renewcommand{\arraystretch}{1}
\end{equation}

The reaction vector is
\begin{equation}
\Rb = \left (  \begin{array}{c} \rho \omegadot_\alpha \\ \rho \omegadot_\beta \\ \rho \Sdot \\ \rho \Sdot \end{array} \right )
\end{equation}
and the Jacobian is computed as $\partial \Rb/\partial {\bf w}$:
\begin{equation}
\frac{\partial \Rb}{\partial {\bf w}} = \left (
  \begin{array}{cccc}
     \omegadot_\alpha + \rho \frac{\partial \omegadot_\alpha}{\partial \rho} &
     \rho \frac{\partial \omegadot_\alpha}{\partial X_\alpha} &
     \rho \frac{\partial \omegadot_\alpha}{\partial X_\beta} & \rho \frac{\partial \omegadot_\alpha}{\partial T} \\
      %
     \omegadot_\beta + \rho \frac{\partial \omegadot_\beta}{\partial \rho} &
     \rho \frac{\partial \omegadot_\beta}{\partial X_\alpha} &
     \rho \frac{\partial \omegadot_\beta}{\partial X_\beta} & \rho \frac{\partial \omegadot_\beta}{\partial T} \\
     %
     \Sdot + \rho \frac{\partial \Sdot}{\partial \rho} & \rho \frac{\partial \Sdot}{\partial X_\alpha} & \rho \frac{\partial \Sdot}{\partial X_\beta} & \rho \frac{\partial \Sdot}{\partial T} \\
     %
     \Sdot + \rho \frac{\partial \Sdot}{\partial \rho} & \rho \frac{\partial \Sdot}{\partial X_\alpha} & \rho \frac{\partial \Sdot}{\partial X_\beta} & \rho \frac{\partial \Sdot}{\partial T} \\
  \end{array}
  \right )
\end{equation}

>>>>

Even though it has no reactive sources, we include $\rho$ in our conservative state
for the purposes of computing the Jacobian (we denote the conserved state used for the
Jacobian $\Uc^\prime$.  
Writing this out for two species, $X_\alpha$ and $X_\beta$, we have
\begin{equation}
\Uc^\prime = \left ( \begin{array}{c} \rho \\ \rho X_\alpha \\ \rho X_\beta \\ \rho E \\ \rho e \end{array} \right )
\end{equation}
We take the intermediate state to be ${\bf w} = (\rho, X_\alpha, X_\beta,
K, T)^\intercal$, where $K$ is the kinetic energy:
\begin{equation}
K = \frac{1}{2} |\Ub|^2
\end{equation}

The Jacobian transformation $\partial \Uc^\prime/\partial {\bf w}$ is:
\begin{equation}
\frac{\partial \Uc}{\partial {\bf w}} = \left (
   \begin{array}{ccccc}
       1 & 0 & 0 & 0 & 0 \\
       X_\alpha & \rho & 0 & 0 & 0 \\
       X_\beta & 0 & \rho & 0 & 0  \\
       \rho e_\rho  + e + K &
                 \rho  e_{X_\alpha} & \rho e_{X_\beta} & \rho &
                 \rho e_T \\
       \rho e_\rho  + e  &
                 \rho  e_{X_\alpha} & \rho e_{X_\beta} & 0 &
                 \rho e_T
     \end{array}\right)
\end{equation}
where we use the following notation for compactness:
\begin{equation}
e_\rho = \dedrd \qquad 
e_T = \dedTd \qquad
e_{X_k} = \dedXd 
\end{equation}
and write the kinetic energy as $K = |\Ub|^2/2$.  We get the inverse
(computed via SymPy, see the included Jupyter notebook) is:

\begin{equation}
\renewcommand{\arraystretch}{1.5}
\frac{\partial {\bf w}}{\partial \Uc^\prime} = \left (
  \begin{array}{ccccc}
   1  & 0 & 0 & 0 & 0 \\
   - \frac{X_\alpha}{\rho} & \frac{1}{\rho} & 0 & 0 & 0 \\
   - \frac{X_\beta}{\rho} & 0 & \frac{1}{\rho} & 0 & 0 \\
   - \frac{K}{\rho} & 0 & 0 & \frac{1}{\rho} & -\frac{1}{\rho} \\
   \frac{\sum_k X_{k} e_{X_k} - \rho e_\rho - e}{ \rho e_T} &
    -\frac{e_{X_\alpha}}{\rho e_T} & -\frac{e_{X_\beta}}{\rho e_T} & 0 & \frac{1}{\rho e_T} \\
   \end{array}\right)
\renewcommand{\arraystretch}{1}
\end{equation}

The reaction vector is
\begin{equation}
\Rb(\Uc^\prime) = \left (  \begin{array}{c} 0 \\ \rho \omegadot_\alpha \\ \rho \omegadot_\beta \\ \rho \Sdot \\ \rho \Sdot \end{array} \right )
\end{equation}
and the Jacobian is computed as $\partial \Rb/\partial {\bf w}$:
\begin{equation}
\frac{\partial \Rb}{\partial {\bf w}} = \left (
  \begin{array}{ccccc}
     0 & 0 & 0 & 0 & 0 \\
     \omegadot_\alpha + \rho \frac{\partial \omegadot_\alpha}{\partial \rho} &
     \rho \frac{\partial \omegadot_\alpha}{\partial X_\alpha} &
     \rho \frac{\partial \omegadot_\alpha}{\partial X_\beta} & 0 & \rho \frac{\partial \omegadot_\alpha}{\partial T} \\
      %
     \omegadot_\beta + \rho \frac{\partial \omegadot_\beta}{\partial \rho} &
     \rho \frac{\partial \omegadot_\beta}{\partial X_\alpha} &
     \rho \frac{\partial \omegadot_\beta}{\partial X_\beta} & 0 &  \rho \frac{\partial \omegadot_\beta}{\partial T} \\
     %
     \Sdot + \rho \frac{\partial \Sdot}{\partial \rho} & \rho \frac{\partial \Sdot}{\partial X_\alpha} & \rho \frac{\partial \Sdot}{\partial X_\beta} & 0 & \rho \frac{\partial \Sdot}{\partial T} \\
     %
     \Sdot + \rho \frac{\partial \Sdot}{\partial \rho} & \rho \frac{\partial \Sdot}{\partial X_\alpha} & \rho \frac{\partial \Sdot}{\partial X_\beta} & 0 & \rho \frac{\partial \Sdot}{\partial T} \\
  \end{array}
  \right )
\end{equation}
